\chapter{Conclusion}
\label{chap:conclusion}

Wireless network technology is a must as it overcomes a big problem for the wired network technology which is the mobility. Wireless technology has overcame the mobility shortage however it still has a big drawback which is the security. Wireless technology still suffers from many kind of attacks due to its open medium nature which makes it vulnerable to intercepting and sniffing and so on. three obstacles faced the wireless technology which are frequency allocation,Interference, Reliability \& Security. Authentication, Association, encryption,encryption mechanisms and attacks were discussed and the conclusion is:

I.The device needs to be authenticated before it starts to use the service of the access point. Three encryption types were discussed which are:
	a.WEP: Uses a 40 bit shared key to encrypt data between the AP and the user.
	b.WPA: Uses a unique key for each user.
	c.WPA2: The main difference was the mandatory use of AES algorithms and the introduction of CCMP as a replacement for TKIP.

II. PEAP is the most commonly used authentication method. EAP-TLS is the most secure while LEAP provides weak security as it vulnerable to dictionary attacks.
III.Dictionary attack ended the WEP era and another types of attacks were discussed.
IV.PKI is able to be effective at securing data over a network. RADIUS in combination with LDAP can handle Authentication, Authorization \& Accounting of a network, and can be modified to deal with custom requirements of different networks.

To sum up Wireless network technology is a great step towards mobility but it needs further security enhancement so it can totally substitute the wired connections.
