\chapter{Introduction}
\label{chap:intro}

Wireless communications are widespread nowadays as a result of it's low installation and maintenance cost compared to wired ones. Wireless technology offers a great solution for users with difficult geographical and environmental factors(Crow,Fujitsu,Kim \& Sakai).

Users need the same level of security, services and capabilities from the wireless technology in order to substitute the wired connection with a wireless one. However the wireless technology faced many obstacles that were not faced with the wired connections (Crow, Fujitsu, Kim \& Sakai). Wireless technology showed a shortage in securing the connection as the signal may be intercepted which lead to security breach (Herbet \& Nou).

The kind of problems that Wireless technology faced are:

\begin{enumerate}
  \item Frequency allocation: In order to make the wireless technology work all the users have to operate on a specific frequency band which must approved and licensed by every country. This operation takes time due to the high demand on a limited radio spectrum(Crow, Fujitsu, Kim \& Sakai).
  \item Interference \& Reliability: Interference is most commonly occurred as a result of simultaneous transmission which result in collisions that affect the wireless technology reliability(Crow, Fujitsu, Kim \& Sakai).
  \item Security: Wired connection is easily secured in compare to wireless and easier to control it's accessibility. Wireless network is more liable to hack due to it's transmission medium. Therefore data encryption is used but it affects the cost and the performance (Crow, Fujitsu, Kim \& Sakai).
\end{enumerate}


In this report Authentication and Association will be discussed and encryption types will be illustrated along with encryption mechanisms. Finally some types of wireless attacks will be explained
